\section{Shooting a Target}\label{sec:shooting}
For this project, the shooting part will be the launch of a projectile, which gives certain challenges when attempting to shoot a moving target. \\

Certain factors have to be considered when firing projectiles at any given target. The most important factors are the velocity of both the target, and of the projectile, as well as the distance to the target and the accuracy of the projectiles. Another important factor is the predictability of the target, mostly in regards to the path which the target will take. However, due to the delimitations to the tower defense scenario in this project, a predictable path is assumed. \\

The properties of the tower that was eventually constructed will be covered in \cref{turret}, but some deductions can be made from the other factors alone.

\subsection{Field of View}\label{FoW}
As the target enters the field of view, the shooting system has a limited time to respond, where the time available depends on the speed of the target. A faster target will leave the field of view quicker, providing a shorter time frame for the projectile to hit the target. If a degree of freedom is assumed in the distance between a tower and a target, the time that target spends in the field of view can be increased at the cost of increasing the travel time of the projectile.\\

The distance from a tower to a given target inside its observable area, is not likely to be constant. In fact this is only the case when the target follows a path which curves in parallel to the tower. Assuming a straight path parallel to a tangent of a towers field of view, the distance to a target will increase in relation to the distance between that target and the tangent's point of contact. This fact, in relation to the velocity of the projectile, limits the maximum distance to the target, and as such also the effective observable area. This can be seen in \cref{25} where $a$ shows the shortest distance to the track, $b$ shows the maximum shooting distance and $c$ shows a distance out of reach. This shows that as $a$ shortens, the effective range increases, but never more than the range of $b$. On the other hand, increasing the field of view by extending $a$, happens at the cost of a diminished observable area.

\begin{figure}[H]
\begin{center}
\begin{tikzpicture}

   \draw [dashed] (3,0) arc (0:180:4cm);
   \draw [thick](-5,3) -- (3,3);
   \draw [-triangle 90,fill=black](-1,0) -- node[left] {a} (-1,3);
   \draw [-triangle 90,fill=black](-1,0) -- node[left] {b} (0.8,3.6);
   \draw [-triangle 90,fill=black](-1,0) -- node[left] {c} (3,3);
   %\draw (-0.9,2.8) -- (-1.1,2.8) --(-1,3) -- (-0.9,2.8);

\end{tikzpicture}
\end{center}
\caption{Illustration of the effective observable area}
\label{25}
\end{figure}
\smallskip

The limit on the time a target spends in the effective range of a tower, also adds a requirement of time to the task of acquiring a target and releasing a projectile. If targets require multiple hits before being eliminated, which is the case in classical tower defense games, this will further increase the emphasis on time, since the faster the projectiles are fired, the sooner that target will be eliminated. However, for the purpose of a game, this could be considered a part of the challenge of managing your tower resources. So a tower should not necessarily have the fastest possible reaction, but rather a consistent one. 

\subsection{Trajectory Prediction}\label{sec:motionprediction}
When firing projectiles the correlation between the ratio of the projectiles travel time, and the time it takes for the target to travel its own length, must be considered. If for example the distance is one meter, and the projectile velocity is one meter per second, a target that moves faster than its own length in a second, will not be hit by a projectile launched directly at the target. If we assume a passing target to move at a pace sufficiently high, such that a tower can not successfully hit the target by firing immediately upon detection, it becomes necessary to be able to predict the movement of the target, and fire the projectile a distance in front of target.\\

In summation, the process of firing a projectile is a time sensitive task, in regards to both how long the target is in the effective range of the tower, how fast a projectile can be released, and how fast a prediction of the trajectory can be made.
\bigskip





%A possible solution for this is measuring the speed and direction of the target, and the distance from the turret to the target, at one fixed point. Based on these measurements the turret should calculate how far the target will travel in a given time frame, and then adjust its aim according to this calculation. As this method bases the calculations on a single measurement, it has certain limitations. It is not able to account for change in the targets speed or direction after the measuring point. In order to circumvent these limitations, another method for measuring characteristics of the target is necessary.

%As the limitations stem from basing the calculations on a single measuring point, other measuring points could be added. As the turret does not know the path of the track beforehand, there is a possibility of the track turning out of the turrets range between measuring points. In order to avoid this, the measuring points can not be too far from each other. A large number of measuring points will increase the precision of the prediction of the targets movement. One possible method to increase the amount of measuring points, is to let the turret continuously track its target, while also measuring the distance.


%This distance depends on several different factors, including the objects speed, the distance from the cannon to the object, and the direction in which the object is moving. In order to calculate this distance, SOMESTUFF will be used.
%\addtodo{Lasse}{What stuff?}
%\addtodo{Lasse}{The angle the cannon has to turn depends on both the calculated distance, and the path of the track.} 
%\eal

%\subsection{SOMESTUFF}



%Below are some examples, that illustrate some of the problems that need to be considered. \\

%\textbf{Example 1} \\
%The turret is placed at a specific distance from the path of the moving target. The faster the target moves the faster it will go past the tracking system. If the turret is moved close to the path of the target the field of view of the tracking system will decrease. This results in a shorter time span in which it's possible to hit the target with a projectile.  \\\\

%\textbf{Example 2} \\
%The target is moving at the same speed at all times and its size does not change. The turret is moved in a straight line towards and away from the path of the target. The farther away the turret is moved, the more important the speed and drop of the projectile becomes. At long ranges the projectile might become inaccurate, partly because the travel time increases. \\\\

%\textbf{Example 3} \\
%The turret is placed at a specific distance from the path of the target. The speed of the target can change at any time. If the turret is placed far away from the path of the target the projectile will have a long travel time. If the speed of the target changes at the moment the projectile is fired, the prediction of the target's location may no longer be accurate which can result in the projectile missing the target.